\newpage

\lstset{
	keywordstyle=\textbf,
	basicstyle=\ttfamily,
	breakatwhitespace=false,
	breaklines=true,
	captionpos=t,
	keepspaces=true,
	numbers=left,
	numbersep=5pt,
	numberstyle=\small\ttfamily,
	extendedchars=true,
	inputencoding=cp1251,
	frame=single,
	tabsize=2,
}

\paragraph{Код:}
Проект на GitHub: \\
\texttt{https://github.com/asurkis/web-lab4} \\

\dirtree{%
.1 lab4/.
.2 backend/.
.3 build.gradle.kts.
.3 src/main/
.4 kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/.
.5 Application.kt.
.6 advices/.
.7 Advices.kt.
.6 assemblers/.
.7 Assemblers.kt.
.6 controllers/.
.7 PointController.kt.
.7 ResultController.kt.
.7 UserController.kt.
.6 data/.
.7 Data.kt.
.6 exceptions/.
.7 Exceptions.kt.
.6 forms/.
.7 Forms.kt.
.6 repositories/.
.7 Repositories.kt.
.6 services/.
.7 UserService.kt.
.4 resources/.
.5 application.properties.
.2 frontend/.
.3 angular.json.
.3 package.json.
.4 src/.
.5 index.html.
.5 styles.css.
.5 app/.
.6 app.component.css.
.6 app.component.html.
.6 app.component.ts.
.6 app.module.ts.
.6 data-types.ts.
.6 shared-data.service.ts.
.6 login/.
.7 login.component.css.
.7 login.component.html.
.7 login.component.ts.
.6 main/.
.7 main.component.css.
.7 main.component.html.
.7 main.component.ts.
.6 register/.
.7 register.component.css.
.7 register.component.html.
.7 register.component.ts.
.6 results-picture/.
.7 results-picture.component.css.
.7 results-picture.component.html.
.7 results-picture.component.ts.
.6 results-table/.
.7 results-table.component.css.
.7 results-table.component.html.
.7 results-table.component.ts.
.6 user-input/.
.7 user-input.component.css.
.7 user-input.component.html.
.7 user-input.component.ts.
}

% lab4/backend/build.gradle.kts
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/Application.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/advices/Advices.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/assemblers/Assemblers.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/controllers/PointController.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/controllers/ResultController.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/controllers/UserController.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/data/Data.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/exceptions/Exceptions.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/forms/Forms.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/repositories/Repositories.kt
% lab4/backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/services/UserService.kt
% lab4/backend/src/main/resources/application.properties
% lab4/frontend/angular.json
% lab4/frontend/package.json
% lab4/frontend/src/index.html
% lab4/frontend/src/styles.css
% lab4/frontend/src/app/app.component.css
% lab4/frontend/src/app/app.component.html
% lab4/frontend/src/app/app.component.ts
% lab4/frontend/src/app/app.module.ts
% lab4/frontend/src/app/data-types.ts
% lab4/frontend/src/app/shared-data.service.ts
% lab4/frontend/src/app/login/login.component.css
% lab4/frontend/src/app/login/login.component.html
% lab4/frontend/src/app/login/login.component.ts
% lab4/frontend/src/app/main/main.component.css
% lab4/frontend/src/app/main/main.component.html
% lab4/frontend/src/app/main/main.component.ts
% lab4/frontend/src/app/register/register.component.css
% lab4/frontend/src/app/register/register.component.html
% lab4/frontend/src/app/register/register.component.ts
% lab4/frontend/src/app/results-picture/results-picture.component.css
% lab4/frontend/src/app/results-picture/results-picture.component.html
% lab4/frontend/src/app/results-picture/results-picture.component.ts
% lab4/frontend/src/app/results-table/results-table.component.css
% lab4/frontend/src/app/results-table/results-table.component.html
% lab4/frontend/src/app/results-table/results-table.component.ts
% lab4/frontend/src/app/user-input/user-input.component.css
% lab4/frontend/src/app/user-input/user-input.component.html
% lab4/frontend/src/app/user-input/user-input.component.ts

\lstinputlisting[title=build.gradle.kts]               {../../backend/build.gradle.kts}
\lstinputlisting[title=application.properties]         {../../backend/src/main/resources/application.properties}
\lstinputlisting[title=Application.kt]                 {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/Application.kt}
\lstinputlisting[title=Advices.kt]                     {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/advices/Advices.kt}
\lstinputlisting[title=Assemblers.kt]                  {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/assemblers/Assemblers.kt}
\lstinputlisting[title=PointController.kt]             {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/controllers/PointController.kt}
\lstinputlisting[title=ResultController.kt]            {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/controllers/ResultController.kt}
\lstinputlisting[title=UserController.kt]              {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/controllers/UserController.kt}
\lstinputlisting[title=Data.kt]                        {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/data/Data.kt}
\lstinputlisting[title=Exceptions.kt]                  {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/exceptions/Exceptions.kt}
\lstinputlisting[title=Forms.kt]                       {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/forms/Forms.kt}
\lstinputlisting[title=Repositories.kt]                {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/repositories/Repositories.kt}
\lstinputlisting[title=UserService.kt]                 {../../backend/src/main/kotlin/ru/ifmo/se/labs/asurkis/lab4/backend/services/UserService.kt}
\lstinputlisting[title=package.json]                   {../../frontend/package.json}
\lstinputlisting[title=angular.json]                   {../../frontend/angular.json}
\lstinputlisting[title=index.html]                     {../../frontend/src/index.html}
\lstinputlisting[title=styles.css]                     {../../frontend/src/styles.css}
\lstinputlisting[title=app.module.ts]                  {../../frontend/src/app/app.module.ts}
\lstinputlisting[title=app.component.css]              {../../frontend/src/app/app.component.css}
\lstinputlisting[title=app.component.html]             {../../frontend/src/app/app.component.html}
\lstinputlisting[title=app.component.ts]               {../../frontend/src/app/app.component.ts}
\lstinputlisting[title=data-types.ts]                  {../../frontend/src/app/data-types.ts}
\lstinputlisting[title=shared-data.service.ts]         {../../frontend/src/app/shared-data.service.ts}
\lstinputlisting[title=login.component.css]            {../../frontend/src/app/login/login.component.css}
\lstinputlisting[title=login.component.html]           {../../frontend/src/app/login/login.component.html}
\lstinputlisting[title=login.component.ts]             {../../frontend/src/app/login/login.component.ts}
\lstinputlisting[title=main.component.css]             {../../frontend/src/app/main/main.component.css}
\lstinputlisting[title=main.component.html]            {../../frontend/src/app/main/main.component.html}
\lstinputlisting[title=main.component.ts]              {../../frontend/src/app/main/main.component.ts}
\lstinputlisting[title=register.component.css]         {../../frontend/src/app/register/register.component.css}
\lstinputlisting[title=register.component.html]        {../../frontend/src/app/register/register.component.html}
\lstinputlisting[title=register.component.ts]          {../../frontend/src/app/register/register.component.ts}
\lstinputlisting[title=results-picture.component.css]  {../../frontend/src/app/results-picture/results-picture.component.css}
\lstinputlisting[title=results-picture.component.html] {../../frontend/src/app/results-picture/results-picture.component.html}
\lstinputlisting[title=results-picture.component.ts]   {../../frontend/src/app/results-picture/results-picture.component.ts}
\lstinputlisting[title=results-table.component.css]    {../../frontend/src/app/results-table/results-table.component.css}
\lstinputlisting[title=results-table.component.html]   {../../frontend/src/app/results-table/results-table.component.html}
\lstinputlisting[title=results-table.component.ts]     {../../frontend/src/app/results-table/results-table.component.ts}
\lstinputlisting[title=user-input.component.css]       {../../frontend/src/app/user-input/user-input.component.css}
\lstinputlisting[title=user-input.component.html]      {../../frontend/src/app/user-input/user-input.component.html}
\lstinputlisting[title=user-input.component.ts]        {../../frontend/src/app/user-input/user-input.component.ts}
